Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition

### 2015-07-13 papers/data_paper/datapaper.tex
mon

\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition}

@@

\begin{abstract}
Several recent studies have performed galaxy decompositions 
to investigate correlations between the black hole mass and the host spheroid properties, 
but they have not converged to the same conclusions. 
This is because their best fit models for the same galaxy were often significantly different 
and not consistent with each other in terms of fitted components. 
Using $3.6 \rm ~\mu m$ \emph{Spitzer} imagery, which is a superb tracer of the stellar mass (superior to the $K$-band), 
we have performed state-of-the-art multicomponent decompositions for 66 galaxies 
with directly measured black hole masses. 
Our sample is the largest to date and, 
unlike previous studies, contains a large number (17) of spiral galaxies with low black hole masses. 
We paid careful attention to the image mosaicking, sky subtraction and masking of contaminating sources.
Thanks to a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- of the 2D kinematics, 
we were able to identify and model bulges, large-scale, intermediate-scale or nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
sources and partially depleted cores. 
For each individual galaxy, we compared our best-fit model with those presented by the previous studies, 
explained the discrepancies and identified the optimal decomposition.
We independently performed 1D and 2D decompositions, 
and concluded that, at least when modelling large, nearby galaxies, 1D techniques have more advantages than 2D techniques. 
Finally, we developed a method to estimate the uncertainties on the 1D best-fit parameters 
that takes into account systematic errors, 
unlike popular 2D codes that only consider statistical errors.

@@

Supermassive black holes and host bulges have very different sizes. 
If the event horizon of the Galactic supermassive black hole was as big as a grain of sand of the Sahara desert, 
then the black hole gravitational sphere-of-influence would be as big as the international airport of Cairo, 

@@

scale with a number of properties of their host bulges, 

@@

marconihunt2003,haringrix2004,graham2012bent,grahamscott2015}). \\
The tightness of (i.e.~the small scatter about) the observed black hole mass correlations has led to the idea
that black holes and host galaxies have coevolved with some sort of self-regulated growth.

@@

the driving mechanisms of the black hole -- galaxy coevolution.

@@

Any complete theory or model describing the coevolution of galaxies and black holes must incorporate 

@@

Such scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct

@@

the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}) 

@@

and as such the recalibration of the black hole mass -- bulge stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large bulges,
from $0.1 - 0.2\%$ (e.g.~\citealt{haringrix2004}) to $0.36\%$ \citep{graham2012bent} and then $0.49\%$ \citep{grahamscott2015}, 

@@

massive galaxies, either quiescent or active. \\
Massive, early-type galaxies are often composite systems. 
The knowledge that many ``elliptical'' galaxies actually contain embedded stellar disks dates back  

@@

\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995}. 

@@

More than half of all morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.

@@

dominate only the most massive end (beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
Given the prevalence of disks, it is clearly important to perform bulge/disk decompositions, 
if one is to properly explore the black hole-bulge connection. 

@@

galaxy component, such as bulges, disks, bars, nuclei, etc.).

@@

in order to derive the bulge parameters and explore their relation with the black hole masses. 

@@

(the bulge S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
whereas the remaining four did not.

@@

declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity and the bulge luminosity, 
as opposed to \cite{beifiori2012}, who claimed that the bulge mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.

@@

using the largest sample (66) of galaxies to date.

@@

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful bulge parameters could be obtained.

@@

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or bulges) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2014cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2015},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
%\caption{Best-fit model and isophotal parameters for the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial bulges can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques.
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful bulge parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
%and are therefore compared to them in Figure \ref{fig:n1d2d}.
%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
\caption{2D versus 1D major-axis measurements of the effective radii. 
The dashed line displays the 1:1 relation.}
\label{fig:re1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
\caption{2D measurements of the S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.}
\label{fig:n1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ bulge magnitudes. The dashed line displays the 1:1 relation.}
\label{fig:mag1d2d}
\end{center}
\end{figure}

\subsection{Parameter uncertainty}
\label{sec:err}
Estimating the uncertainties associated with the best-fit parameters of our 1D galaxy decompositions is not straightforward.
Monte Carlo simulations could be used for this purpose, 
but they would take into account only random errors and not unknown systematic errors.
Systematic errors include incorrect sky subtraction, 
inaccurate masking of contaminating sources, 
imprecise description of the PSF, 
erroneous choice of model components 
(for example, when failing to identify a galaxy sub-component and thus omitting it in the model, 
or when describing a galaxy sub-component with an inadequate function),
the radial extent of the surface brightness profile and its sampling.
These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters.  
Moreover, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
errors are dominated by systematics rather than Poisson noise.
For this reason, we decided to estimate the uncertainties of the bulge best-fit parameters 
with a method that took into account systematic errors.

>>>>

\title{Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition}

@@

\begin{abstract}
Several recent studies have performed galaxy decompositions 
to investigate correlations between the black hole mass and various properties of the host spheroid, 
but they have not converged on the same conclusions. 
This is because their models for the same galaxy were often significantly different 
and not consistent with each other in terms of fitted components. 
Using $3.6 \rm ~\mu m$ \emph{Spitzer} imagery, which is a superb tracer of the stellar mass (superior to the $K$-band), 
we have performed state-of-the-art multicomponent decompositions for 66 galaxies 
with directly measured black hole masses. 
Our sample is the largest to date and, 
unlike previous studies, contains a large number (17) of spiral galaxies with low black hole masses. 
We paid careful attention to the image mosaicking, sky subtraction and masking of contaminating sources.
After a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- 2D kinematics, 
we were able to account for spheroids, large-scale, intermediate-scale and nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
sources and partially depleted cores. 
For each individual galaxy, we compared our best-fit model with previous studies, 
explained the discrepancies and identified the optimal decomposition.
Moreover, we have independently performed 1D and 2D decompositions, 
and concluded that, at least when modelling large, nearby galaxies, 1D techniques have more advantages than 2D techniques. 
Finally, we developed a prescription to estimate the uncertainties on the 1D best-fit parameters for the 66 spheroids 
that takes into account systematic errors, 
unlike popular 2D codes that only consider statistical errors.

@@

Supermassive black holes and their host spheroids\footnote{The term ``spheroid'' refers to either an elliptical galaxy or the spheroidal component 
of a galaxy with a disk. } 
have very different sizes. 
If the event horizon of the Galactic supermassive black hole was as big as a grain of sand in the Sahara desert, 
then the black hole's gravitational sphere-of-influence would be as big as the international airport of Cairo, 

@@

scale with a number of properties of their host spheroid, 

@@

marconihunt2003,haringrix2004,grahamscott2015}). \\
The tightness of (i.e.~the small scatter about) the above observed black hole mass correlations has led to the idea
that black holes and host spheroids have coevolved with some sort of self-regulated growth.

@@

the driving mechanisms of the black hole -- spheroid coevolution.

@@

Any complete theory or model describing the coevolution of spheroids and black holes must incorporate 

@@

The observed scaling relations can also be employed to predict the masses of black holes in other galaxies, where a direct

@@

the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}; Fontanot et al. \emph{submitted}) 

@@

and as such the recalibration of the black hole mass -- spheroid stellar mass ratio ($M_{\rm BH}/M_{\rm *,sph}$) in large spheroids,
from $0.1 - 0.2\%$ (e.g.~\citealt{marconihunt2003,haringrix2004}) to $0.49\%$ \citep{grahamscott2015}, 

@@

massive spheroids, either quiescent or active. \\
Massive, early-type (E, E/S0, S0) galaxies are often composite systems. 
The knowledge that many ``elliptical'' (E) galaxies were misclassified and actually contain embedded stellar disks dates back  

@@

\citep{capaccioli1987,carter1987,rixwhite1990,rixwhite1992,bender1990,scorzabender1990,nieto1991,scorzabender1995}. 

@@

Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.

@@

dominate only the most massive end (with stellar masses beyond $10^{11.5}~\rm M_\odot$) of the distribution. 
Given the prevalence of disks, it is clearly important to perform spheroid/disk decompositions, 
if one is to properly explore the black hole -- spheroid connection. 

@@

galaxy component, such as spheroids, disks, bars, nuclei, etc.).

@@

in order to derive the spheroid parameters and explore their relation with the black hole masses. 

@@

(the spheroid S\'ersic index $n_{\rm sph}$ is a measure of the central radial concentration of stars, \citealt{trujillo2001}), 
whereas the remaining four did not\footnote{\cite{savorgnan2013} showed that, 
by rejecting the most discrepant S\'ersic index measurements and averaging the remaning ones, 
a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. 
The fact that none of the four studies obtained a significant $M_{\rm BH}-n_{\rm sph}$ correlation with their individual measurements 
is indicative of non accurate galaxy decompositions. }.

@@

declared that $M_{\rm BH}$ correlates equally well with the total galaxy luminosity as it does with the spheroid luminosity, 
as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.

@@

using the largest sample (66) of galaxies to date with accurate spheroid properties. \\

@@

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful spheroid parameters could be obtained.

@@

\subsubsection{S\'ersic/core-S\'ersic classification}
\label{sec:corser}
Core-S\'ersic galaxies \citep{grahamguzman2003,graham2003coresersicmodel,trujillo2004coresersicmodel} are galaxies (or spheroids) 
with partially depleted cores, 
i.e.~a central deficit of light relative to the inward extrapolation of their outer S\'ersic light profile. 
Such deficits were first noted and researched by \cite{kingminkowski1966}.
S\'ersic galaxies, instead, do not exhibit such central stellar deficits.
Partially depleted cores, as measured from high-resolution observations, have typical sizes of a few tens of parsecs
\citep{dullograham2014cores,rusli2013}.
The majority are thus unresolved in our image mosaics. 
We masked these unresolved cores (identified in high-resolution images, see Table \ref{tab:sample}) by excluding the surface brightness profile 
within 3 PSF's $FWHM$ from the galaxy center.
In case of cores with sizes exceeding the PSF's $FWHM$, we excluded the data points within the size of the core 
plus 3 PSF's $FWHM$.
The S\'ersic/core-S\'ersic classification presented in this work (Table \ref{tab:sample}, column 5)
comes from the compilation of \citet{savorgnangraham2015},
who identified partially depleted cores according to the same criteria used by \citet{grahamscott2013}.
When no high-resolution image analysis was available from the literature, 
they inferred the presence of a partially depleted core based on the stellar velocity dispersion, $\sigma$:
a galaxy is classified as core-S\'ersic if $\sigma > 270\rm~km~s^{-1}$,
or as S\'ersic if $\sigma < 166\rm~km~s^{-1}$.
This resulted in us assigning cores to just 2 galaxies using this alternative method when 
no high resolution image was available.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
%\caption{the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
%\caption{the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
%\caption{the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial spheroids can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques.
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful spheroid parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
%and are therefore compared to them in Figure \ref{fig:n1d2d}.
%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
\caption{2D versus 1D major-axis measurements of the spheroid effective radii. 
The dashed line displays the 1:1 relation.}
\label{fig:re1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.}
\label{fig:n1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ spheroid magnitudes. The dashed line displays the 1:1 relation.}
\label{fig:mag1d2d}
\end{center}
\end{figure}

\subsection{Parameter uncertainty}
\label{sec:err}
Estimating the uncertainties associated with the best-fit parameters of our 1D galaxy decompositions is not straightforward.
Monte Carlo simulations could be used for this purpose, 
but they would take into account only random errors and not unknown systematic errors.
Systematic errors include incorrect sky subtraction, 
inaccurate masking of contaminating sources, 
imprecise description of the PSF, 
erroneous choice of model components 
(for example, when failing to identify a galaxy sub-component and thus omitting it in the model, 
or when describing a galaxy sub-component with an inadequate function),
the radial extent of the surface brightness profile and its sampling.
These factors are not included in popular 2D fitting codes which report only the random errors associated with their fitted parameters.  
Moreover, when performing multi-component decomposition of high signal-to-noise images of nearby -- therefore well resolved -- galaxies, 
errors are dominated by systematics rather than Poisson noise.
For this reason, we decided to estimate the uncertainties of the spheroid best-fit parameters 
with a method that took into account systematic errors.

\subsubsection{Goodness of the spheroid modeling}
For each of our fits, we calculated the associated $RMS$ scatter using:
\begin{equation}
\Delta = \sqrt{\frac{\sum_{\rm i=0}^{N} (\mu_{\rm i}^{\rm obs} - \mu_{\rm i}^{\rm mod})^2}{N_{\rm DOF}} } ,
\end{equation} 
where $N_{\rm DOF}$ is the number of degrees-of-freedom, 
$\mu_{\rm i}^{\rm obs}$ is the observed surface brightness 
and $\mu_{\rm i}^{\rm mod}$ is the model surface brightness at each data point $i$.
Although useful to evaluate the overall quality of a galaxy decomposition, 
the $RMS$ scatter alone cannot be used to assess the goodness of the fit for the spheroidal component only, 
unless the galaxy is a pure spheroid and has consequently been modeled with a single S\'ersic profile.
To illustrate this point with an example, 
one can imagine a situation in which a galaxy is thought to be made of a small bulge and a much more extended disk.
This galaxy is decomposed with a S\'ersic + exponential model.
The exponential function provides an excellent description of the light profile of the disk, 
whereas the S\'ersic function does not do the same for the bulge.
The residuals of the fit will then be flat and close to zero at large radii, 
where the emission of the disk dominates over that of the bulge,
while they will display significant departures at small radii, 
in correspondence with the poorly fit spheroidal component.
In the case of linear sampling, 
because the part of the surface brightness profile pertaining to the disk may contain more data points 
than the part pertaining to the bulge, 
the global $RMS$ scatter will be relatively small, 
but it obviously will not reflect the accuracy of the fit to the spheroidal component only. \\
A simple but powerful way to get a feeling of how precisely the global model and its spheroidal component have fared
is to look at the major- and equivalent-axis fits of each galaxy 
and visually inspect the structures of the residual surface brightness profile 
(i.e.~the second row in Figure \ref{fig:n2974ex}) within $\sim 1 - 2$ spheroid effective radii. 
We did this using a grade from 1 to 3, assigned according to the following criteria.
\begin{itemize}
\item [1)] A grade of 1 was given to the best fits, i.e.~fits that do not exhibit any of the problems listed below.
\item [2)] A grade of 2 was issued in the following cases. 
The residuals in correspondence with the radial extent of the spheroidal component are not randomly distributed around zero, 
being symptomatic of a S\'ersic model having a curvature (regulated by the S\'ersic index $n$) 
that does not quite match the real ``shape'' of the spheroid. 
When we identified, but were not able to accurately model. a galaxy sub-component.
In the case of apparent inconsistencies between the model and the observed galaxy properties 
(e.g.~an embedded disk modeled with an exponential function, 
whose scale length does not quite match the size of the disk as expected from the ellipticity profile or the velocity map).
When the S\'ersic model used to describe the spheroidal component has a size -- as measured by the effective radius -- 
comparable to a few times the $FWHM$ of the PSF.
Galaxies in this category are reasonably well fit despite these issues.
\item [3)] A grade of 3 was assigned to the poorer and more anomalous fits, 
or those affected by an obvious degeneracy between the spheroid S\'ersic profile and the remaining model components 
(e.g.~when the spheroid S\'ersic index varies by as much as 50\% among the four different realizations of the fit, 
or when the output of the fit strongly depends on the choice of the initial parameters).
\end{itemize}
As a result, we classified 27 galaxies (38\% of the 72 galaxies for which we attempted a 1D decomposition) with grade 1, 
29 galaxies (40\%) with grade 2 and 10 galaxies (14\%) with grade 3.
Six galaxies could not be modelled.
We report the assigned grades in Table \ref{tab:fitres} (column 10).

\subsubsection{Uncertainties on $n_{\rm sph}$}
%\label{sec:sigman}
In Figure \ref{fig:compn}, for 58 galaxies, 
we compare the measurements of the spheroid S\'ersic index obtained by different authors 
with those obtained by us. 
For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of the available measurements, 
and we plot it against the scatter of the individual measurements around each spheroid's $\langle \log(n_{\rm sph}) \rangle$.
The measurements are heterogeneous, 
in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
and they refer either to the major-axis, the equivalent-axis or some 2D average.
In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
for our measurements. 
38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
78\% lie within $-\sigma_2^- = -0.21~\rm dex$ and $+\sigma_2^+ = +0.17~\rm dex$,
and 92\% lie within $-\sigma_3^- = -0.25~\rm dex$ and $+\sigma_3^+ = +0.25~\rm dex$. 
We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. \\
